\section{Introduction}
\label{sec:intro}

In this report, we deal with the low-rank approximation problem.
Given an $n\times d$ matrix $A$,
we would like to find a matrix $\tilde{A}_k$,
such that
\begin{equation}
    \| A - \tilde{A}_k \| \le (1+\varepsilon) \| A - A_k \|,
\end{equation}
where $A_k$ is the best rank-$k$ approximation oto $A$,
and $\tilde{A}_k$ has rank $k$.
The best approximation $A_k$ can be computed by a svd operation.
However, the time required would be huge.
We tested several approximation methods using the sketching technique,
both in the Frobenius norm and the operator norm settings.

\subsection{Dataset}

We use the MovieLens 20M dataset~\cite{lens} as benchmark,
which can be downloaded at~\cite{movielens}.
It contains 20,000,263 5-star ratings on 26744 movies from 138493 users.
This is a typical dataset for the study of recommendation systems.
The low rank nature for the problem is that the contributing factors
for users' preference on a movie is not that much.
Factors like genre, director, actors, etc might dominate one's selection.
The data is also sparse
since the number of movies that a user can reach is limited.
We put all ratings in a sparse matrix
\begin{equation}
    A \in \real^{26744\times 138493},
\end{equation}
with rows be different movies and columns represent users.
There are 20,000,263 (5.4\%) none-zero entries,
and all elements range in $[0, 5]$.

\subsection{Experiment Setting}

All experiments were conducted on a machine that contains an 16-core
Intel Xeon E5-2637 v2 CPU at 3.5GHz, and 256G memory.
Codes were implemented using the Julia language and are available at
https://github.com/innerlee/random.computation.report1.
